Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-07 paper/paper.tex
features

\begin{compactdesc}
\item[POS $n$-grams] Part-of-speech $n$-grams were used in various
  text-classification tasks.
\item[Prompt] Since the prompt contributes information on the domain,
  it is likely that some words (and, hence, character sequences) will
  occur more frequently with some prompts than with others. We
  therefore use the prompt ID in conjunction with other features.
\item[Document length] The number of tokens in the text is highly
  correlated with the author's level of fluency, which in turn is
  correlated with the author's L1.
\item[Pronouns] The use of pronouns varies greatly among different
  authors. We use the same list of~25 English pronouns that
  \citet{vered:noam:shuly} use for identifying translationese.
\item[Punctuation] Similarly, different languages use punctuation
  differently, and we expect this to taint the use of punctuation in
  non-native texts. Of course, character $n$-grams subsume this feature.
\item[Passives] English uses passive voice more frequently than other
  languages. Again, the use of passives in L2 can be correlated with
  the author's L1.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the author's L1.
\item[Cohesive markers] These are 40 function words (and short
  phrases) that have a strong discourse function in texts (\textnl{however},
  \textnl{because}, \textnl{in fact}, etc.) Translators tend to spell out implicit
  utterances and render them explicitly in the target text
  \citep{Blum-Kulka:1986}. We use the list
  of~\citet{vered:noam:shuly}.
\item[Cohesive verbs] This is a list of manually compiled verbs that
  are used, like cohesive markers, to spell out implicit utterances
  (\textnl{indicate}, \textnl{imply}, \textnl{contain}, etc.)
\item[Function words] Frequent tokens, which are mostly function
  words, have been used successfully for various text classification
  tasks. \citet{koppel-ordan:2011:ACL-HLT2011} define a list of 400
  such words, of which we only use~100 (using the entire list was not
  significantly different). Note that pronouns are included in this list.
\item[Contextual function words] To further capitalize on the ability
  of function words to discriminate, we define pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. We also define 3-grams
  consisting of one or two function words and the POS tag of the third
  word in the 3-gram.
\item[Lemmas] The content of the text is not considered a good
  indication of the author's L1, but many text categorization tasks
  use lemmas (more precisely, the stems produced by the tagger) as
  features approximating the content.
\item[Misspelling features] Clearly, the spelling errors that learners
  make in English depend on the phonological properties of their
  L1. \sw{???}
\item[Restored tags] We focus on three important token classes defined
  above: punctuation marks, function words and cohesive verbs. We
  first remove words in these classes from the texts, and then recover
  the most likely hidden tokens in a sequence of words, according to
  an $n$-gram language model trained on all essays in the training
  corpus corrected with a spell checker and containing both words and
  hidden tokens. This feature should capture specific words or
  punctuation marks that are consistently omitted (deletions), or
  misused (insertions, substitutions). To restore hidden tokens we use
  the \texttt{hidden-ngram} utility provided in SRILM
  \citep{stolcke02srilm}.
\item[Brown clusters] \sw{???}
\end{compactdesc}

>>>>

\begin{compactdesc}
\item[POS $n$-grams] Part-of-speech $n$-grams were used in various
  text-classification tasks.
\item[Prompt] Since the prompt contributes information on the domain,
  it is likely that some words (and, hence, character sequences) will
  occur more frequently with some prompts than with others. We
  therefore use the prompt ID in conjunction with other features.
\item[Document length] The number of tokens in the text is highly
  correlated with the author's level of fluency, which in turn is
  correlated with the author's L1.
\item[Pronouns] The use of pronouns varies greatly among different
  authors. We use the same list of~25 English pronouns that
  \citet{vered:noam:shuly} use for identifying translationese.
\item[Punctuation] Similarly, different languages use punctuation
  differently, and we expect this to taint the use of punctuation in
  non-native texts. Of course, character $n$-grams subsume this feature.
\item[Passives] English uses passive voice more frequently than other
  languages. Again, the use of passives in L2 can be correlated with
  the author's L1.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the author's L1.
\item[Cohesive markers] These are 40 function words (and short
  phrases) that have a strong discourse function in texts (\textnl{however},
  \textnl{because}, \textnl{in fact}, etc.) Translators tend to spell out implicit
  utterances and render them explicitly in the target text
  \citep{Blum-Kulka:1986}. We use the list
  of~\citet{vered:noam:shuly}.
\item[Cohesive verbs] This is a list of manually compiled verbs that
  are used, like cohesive markers, to spell out implicit utterances
  (\textnl{indicate}, \textnl{imply}, \textnl{contain}, etc.)
\item[Function words] Frequent tokens, which are mostly function
  words, have been used successfully for various text classification
  tasks. \citet{koppel-ordan:2011:ACL-HLT2011} define a list of 400
  such words, of which we only use~100 (using the entire list was not
  significantly different). Note that pronouns are included in this list.
\item[Contextual function words] To further capitalize on the ability
  of function words to discriminate, we define pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. We also define 3-grams
  consisting of one or two function words and the POS tag of the third
  word in the 3-gram.
\item[Lemmas] The content of the text is not considered a good
  indication of the author's L1, but many text categorization tasks
  use lemmas (more precisely, the stems produced by the tagger) as
  features approximating the content.
\item[Misspelling features] Learning to perceive, produce, and encode non-native phonemic contrasts is extremely difficult for L2 learners \citep{hayes-harb:2008}. Since English's orthography is largely phonemic---even if it is irregular in many places, we expect leaners whose native phoneme contrasts are different from those of English to make characteristic spelling errors. For example, since Japanese and Korean lack a phonemic /l/-/r/ contrast, we expect native speakers of those languages to be more likely to make spelling errors that confuse {\tt l} and {\tt r} relative to native speakers of languages such as Spanish in which that pair is contrastive. To make this information available to our model, we use a noisy channel spelling corrector \citep{kernighan:1990} to identify and correct misspelled words in the training and test data. From these corrections, we extract minimal edit features that show what insertions, deletions, substitutions and joinings (where two separate words are written merged into a single orthographic token) were made by the author of the essay.
\item[Restored tags] We focus on three important token classes defined
  above: punctuation marks, function words and cohesive verbs. We
  first remove words in these classes from the texts, and then recover
  the most likely hidden tokens in a sequence of words, according to
  an $n$-gram language model trained on all essays in the training
  corpus corrected with a spell checker and containing both words and
  hidden tokens. This feature should capture specific words or
  punctuation marks that are consistently omitted (deletions), or
  misused (insertions, substitutions). To restore hidden tokens we use
  the \texttt{hidden-ngram} utility provided in SRI's language modeling toolkit
  \citep{stolcke02srilm}.
\item[Brown clusters] \cite{brown:cl1992} describe an algorithm that induces a hierarchical clustering of a language's vocabulary based on each vocabulary item's tendency to appear in similar left and right contexts in a training corpus. While originally developed to reduce the number of parameters required in $n$-gram language models, Brown clusters have been found to be extremely effective as lexical representations in a variety of regression problems that condition on text \citep{koo:2008,turian:acl2010,owoputi:2013}.  Using an open-source implementation of the algorithm,\footnote{\url{https://github.com/percyliang/brown-cluster}} we clustered 8~billion words of English into 600~classes.\footnote{\url{http://www.ark.cs.cmu.edu/cdyer/en-600/cluster_viewer.html}}  We included log counts of all $4$-grams of Brown clusters that occurred at least $100$ times in the NLI training data.

\end{compactdesc}
